Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-07 paper/main.tex
Title improvement(?)
Should have little impact on the manuscript itself
rewrite intro

% title has to be < 110 chars incl. spaces at the moment 109 Chars
\title{A matter of operationalization: Paradigm and stimulus [feature] selection
impacts localization of "parahippocampal place area"}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize spatial perception in
14 subjects that were watching an audio-visual Hollywood movie and listened to
the audio-description of the same movie (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we further test if an auditory narrative
could substitute localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on stimulus annotations
/ selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants
\citep{sengupata2016extension}.
% results: group AV
On a group level, results of our current approach to operationalize the
perception of space during a movie reveal significantly increased hemodynamic
activity spatially overlapping with the PPA but also extending into early visual
cortices.
% results: group AD
Results of the audio-description reveal significant activation restricted to the
anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provides further evidence that the PPA can be divided into
functional subregions.
% localizer substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.\todo{very bold claim to be written
in the abstract}

@@

\noindent Abstract:

\begin{itemize}
\item missing: the exact (!) presumed PPA function? spatial perception, scene
    representation, spatial layout hypothesis, associative processing? the list
    is endless when it comes what the PPA processes exactly (in pictures)
\item operationalization in two naturalistic stimuli (ecological validity not
    mentioned anymore)
\item AV: ?
\item AD: also as functional localizers
\item Results: ``spatial perception'' can differently operationalized via
    naturalistic stimuli -> we get similar results; AD is restricted to
    anterior PPA; narrative as ``visual localizer''(??)
\end{itemize}

@@

\begin{itemize}
\item presumed function of the PPA? -> spatial layout hypothesis and,
    unfortunately, others
\item question: is localization of proposed PPA function using visual localizer
    valid?
\item why do we use three datasets? To answer question (of presumed function of
    PPA?) that is usually operationalized using pictures (but: big controversy
what exactly in pictures the PPA processes; Aminoff tries to unify the
    arguments)
\item VIS: connection to literature; problem: stimulus validity re PPA function
\item AV: more ecologically valid; problem: of operationalization; why did we do
    it the done way (-> probably issue of method section)
\item AD: alternative stimulus for proposed function but verbal/semantic
    information
\end{itemize}

@@

\begin{itemize}
\item key strategy to address this question
\item which specific cognitive processing do we contrast in AD vs. AV?
\item ``ingredients'' to make it happen? we have some annotations at hand;
    define congruent contrasts based on regressors that are built from
    annotations; available annotations could be described in a dedicated
    section (COH: should be shorty and very high-level; details probably will
    confuse the shit out of readers)
\item what do we need to check to ensure subsequent analyses are valid (COH:
    this is the part that is the most elusive to me when it comes to precise
    phrasing)? a) correlation of regressors, b) negative controls
\end{itemize}

@@

% Open research question
In this study, we investigate if increased hemodynamic activity in the PPA
correlates with ``spatial information'' presented under more ecologically valid
conditions.
% we are different We used two naturalistic
Therefore, we annotated perceptual information embedded in two [perceptual]
rich/multidimensional and continuous naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews):
% audio-description
a) the audio-description (AD) of the Hollywood movie ``Forrest Gump'',
and
% audio-visual
b) the original audio-visual (AV) movie.
% studyforrest dataset
We then analyzed corresponding fMRI data from the same subjects that listened
to the audio-description and watched the audio-visual movie as part of the
publicly available studyforrest dataset
(\href{http://www.studyforrest.org}{studyforrest.org}).
% first: group level AD
First on a group average level, general linear model (GLM) contrasts based on
the audio-description's annotation are used to test if spatial information
embedded in an exclusively auditory stimulus correlates with increased
hemodynamic activity in the PPA that we defined using a block-designed visual
localizer experiment done with the same subjects \citep{sengupta2016extension}.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to GLM results based on the annotation of the movie.
% individual results
Lastly on the level of individual subjects and focussing on the
audio-description [as a possible substitute for a visual localizer], we compare
results of the naturalistic stimuli to results of the visual localizer
\citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract, intro to
discussion and conclusion} Our results demonstrate that (a), (b), (c).

@@

>>>>

% title has to be < 110 chars incl. spaces at the moment 106 Chars
\title{Processing of visual and non-visual naturalistic spatial information in
  the "parahippocampal place area"}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize spatial perception in
14 subjects that were watching an audio-visual Hollywood movie and listened to
the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we further test if an auditory narrative
could localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on stimulus annotations
/ selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants
\citep{sengupata2016extension}.
% results: group AV
On a group level, results of our current approach to operationalize the
perception of space during a movie reveal significantly increased hemodynamic
activity spatially overlapping with the PPA but also extending into early visual
cortices.
% results: group AD
Results of the audio-description reveal significant activation restricted to the
anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provides further evidence that the PPA can be divided into
functional subregions.
% localizer substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.\todo{very bold claim to be written
in the abstract}

@@

@@

\begin{itemize}
\item Struktur des letzten Absatzes finde ich
    bisher nicht so geil (Hypothesen kommen recht spät (d.h. nach Methode),
    Results folgen direkt darauf
\end{itemize}

@@

\begin{itemize}
\item key strategy to address this question
\item auch VIS hat mehrere Kontraste
\item neuer Abschnitt 2.6: all regressoren und Kontraste; Kontraste sind abiträr
    aber ist ok; 2.7: eigentliche Statistische Analyse
\item which specific cognitive processing do we contrast in AD vs. AV?
\item ``ingredients'' to make it happen? we have some annotations at hand;
    define congruent contrasts based on regressors that are built from
    annotations; available annotations could be described in a dedicated
    section (COH: should be shorty and very high-level; details probably will
    confuse the shit out of readers)
\item what do we need to check to ensure subsequent analyses are valid (COH:
    this is the part that is the most elusive to me when it comes to precise
    phrasing)? a) correlation of regressors, b) negative controls
\end{itemize}

\noindent Results

\begin{itemize}
\item mehrere Kontraste in VIS genommen, hier einer berichtet: Teil aus
    Discussion in Results hochnehmen
\end{itemize}

\noindent Discussion
\begin{itemize}
    \item \citep{bartels2004mapping, hasson2004intersubject}
    \item VIS: "best contrast was chosen"
\end{itemize}

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed by
contrasting selected stimulus features that incidentially occur under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
Based on these annotations, we created several general linear model (GLM)
contrast to analyze the corresponding publicly available fMRI datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.
% varying amount of data
Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{rewrite if it should be
mentioned}

% hypo a
We hypothesize[d] that whole-brain analyses will/would reveal increased
hemodynamic activity in the PPA as functionally defined by a visual localizer
experiment using static pictures done with the same subjects
\citep{sengupta2016extension}.
% hypo b
Focussing on the [``cleaner operationalization'' of the] audio-description, we
further hypothesize[d] that an exclusively auditory stimulus can/could
substitute a block-design experiment using pictures to localize a ``visual
area'' in individual subjects.
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions as a block-designed
visual localizer experiment.\todo{interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lasty, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

\todo[inline]{the topic anteriorer vs. posterior is mentioned first at the very
and of the intro and occurrs as "surprising" in the intro as in our results
(it's mentioned in the abstract though)}

@@

\todo[inline]{figure caption: mention / explain other clusters}
